%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

 \cventry
    {Intern} % Job title
    {Admatic Solution Pvt. Ltd.,} % Organization
    {Adyar,Chennai-600009} % Location
    {Apr 2019 - Present (2 months)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Admatics is a start-up company for Data science and Machine Learning. It aims to bring automation in every aspect of daily life.}
        \item {Worked on a project called 'Interactive Vision'. It aims to eliminate the need for for 
        instructor to teach simple mathematics and makes studying more interactive.}
        \item {Trained ICR model for hand written character recognition. Worked on Stereo Vision to  reconstruct of 3D models by generating point cloud images. Gained experience in various topics of computer vision and implemented it in both Python and C++  }
        %\item {Trained OCR to recognize the characters in the number plate after segmentation. }
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Project Assistant} % Job title
    {ACI Automation Pvt. Ltd.,} % Organization
    {255, 2nd Main road, Nehru Nagar,
Kottivakkam(OMR),
Chennai - 96} % Location
    {Dec 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working with Professor Dr. T.T. Mirnalinee and Dr. P. Mirunalini to create a Automatic Number plate Recognition System(APNR).}
        \item {Build a model that uses both image processing technique and Deep learning techniques to locate the number plate in the given image or given frame of a video.}
        \item {Trained OCR to recognize the characters in the number plate after segmentation. }
      \end{cvitems}
    }
    
\end{cventries}