%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Project Team Member} % Role
    {GeoLifeClef ({\tiny https://github.com/nandahkrishna/GeoLifeCLEF2019})} % Event
    {} % Location
    {Mar 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {This is a research project for a competition conducted as a part of International conference (ImageClef)}
        \item{The aim of the research is to find the occurrence  of all species for the particular latitude and longitude  }
        \item{Out of 54 submissions made all of our submission were placed in top 30, and our best submission got 6th rank}
        \item{Our working notes paper got a valuation score of 3 (strong accept). }
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {Project Assistant } % Role
   {Automatic Number Plate Recognition System ({\tiny github.com/pbcpraveen/NumberPlateRecognition})}% Event
    {} % Location
    {Dec 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {APNR is a model that aims to automate the entry of the vehicle information in the data base}
        \item{The model locates the exact location of the number plate in the given image and recognizes it}
         \item{The project employees two CNN models , one to validate the selection of number plate from the image and another for the Optical Character Recognition (OCR) part.}
      \end{cvitems}
      }
\cventry    
    {Team Memeber}
    {Publication Record}
    {}
    {April 2019 - May 2019}
    {
     \begin{cvitems} % Description(s)
        \item {It a website designed to organize all the information of the research papers publish in a well structured manner. }
        \item{Each faculties were give their own unique portal to make submission of their work. It also provide an easy way to search the required records based on keywords from papersror period in which the paper was published or the name of person who published the paper.}
          \item {My role in this project was to pre-process the all old record to make it easy to store in mysql database and also helped to create a database scheme for the project. }
      \end{cvitems}
      
    }

\cventry
    {Personal}
    {Flight Delay Prediction({\tiny https://drive.google.com/drive/u/0/folders/16mosiQ5M9Zx-mxfexw0lhBbyKfjrAc-h})}
    {}
    {Jan 2019 - Present}
    {
     \begin{cvitems} % Description(s)
        \item {This is a research project that aims to predict the delay of the fight based on the weather condition and time of departure }
        \item{There are two different dataset containing the information of flight and weather. The task is merge these two datasets and preprocess them such that it is applicable to the model used for classification and regression task. }
      \end{cvitems}
    }





\cventry
    {Team Memeber}
    {Machine Hand: Arduino}
    {}
    {Sep 2018}
    {
     \begin{cvitems} % Description(s)
        \item {Machine hand is an Arduino project that translates the motion of human hand into a robot hand. }
        \item{The Data required for simulation is collected from a IMU sensor that is attached to a person's hand and the motion is simulated by a servo attached to the robot hand.}
      \end{cvitems}
    }



\cventry
    {Team Memeber}
    {Tic-Tac-Toe: Android Application}
    {}
    {Oct 2018}
    {
     \begin{cvitems} % Description(s)
        \item {Tic-Tac-Toe is our take on the classic game tic toc toe. }
        \item{The game offers a single playes mode with 5 level of difficulties.}
      \end{cvitems}
    }



\cventry
    {Team Leader}
    {Air Hockey: Game in C++({\tiny github.com/pbcpraveen/Air-Hockey})}
    {}
    {Nov 2016 - Jan 2017}
    {
     \begin{cvitems} % Description(s)
        \item {Air Hockey is a our take on the game commonly played in many amusement places.}
        \item{The project employees C-garphics and a C++ file handling system to give absolute smoothness in the working }
           \item{The game also provides a single player mode with 4 varying level of difficulties.}
      \end{cvitems}
    }



\end{cventries}